Liveness-Based Garbage Collection for Lazy Languages

### 2015-11-28 paper/paper.tex
latest - 28th

\begin{lemma}\ref{lemma:grammar-from-analysis-undecidable}
Consider    a    grammar    $G$    of   the    kind    described    in
Definition~\ref{def:specialgrammar}  that  is  generated  by  liveness
analysis  of a  program,  and  a forward  access  path $\alpha$.   The
membership problem $\alpha\$ \in \mathscr{L}(G)$ is undecidable.
\end{lemma}

@@

If there more than one productions with the same LHS, then the
corresponding function creates joins them with a $\SIF$.   If there
are $n$ such functions,  then \mainpgm\  creates  a $n$-way
branch  and inserts  a  single call  to a  distinct  function in  each
branch. It can  be verified that the relevant part  of the grammar for
the production $\nont{i}{c} \rightarrow
c \nont{j}{\acar}\bcar$ shown earlier is:

>>>>

\begin{lemma}\label{lemma:grammar-from-analysis-undecidable}
Consider    a    grammar    $G$    of   the    kind    described    in
Definition~\ref{def:specialgrammar}  that  is  generated  by  liveness
analysis  of a  program,  and  a forward  access  path $\alpha$.   The
membership problem $\alpha\$ \in \mathscr{L}(G)$ is undecidable.
\end{lemma}

@@

\input{equivalent-program}

If there more than one productions with the same LHS, then the
corresponding function creates joins them with a $\SIF$.   If there
are $n$ such functions,  then \mainpgm\  creates  a $n$-way
branch  and inserts  a  single call  to a  distinct  function in  each
branch. It can  be verified that the grammar for the function shown
above, includes the productions:
\begin{align*}
\nont{i}{\acar} &\rightarrow \acar\nont{j}{\acar}\bcar\nont{all}{} \\
\nont{i}{\acar} &\rightarrow \clazy\nont{i}{\acar}\bcar\nont{all}{} \\
\nont{all}{} &\rightarrow \epsilon \mid \acar\nont{all}{} \mid
\acdr\nont{all}{}
\end{align*}
